### 2023-03-21 manuscript.Rmd
Refactor `plot_tfr`

```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"),
  p_cluster = p_cluster
)
```

@@

```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"),
  p_cluster = p_cluster
)
```

@@

```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs5, cache=!run$figures, fig.height=11, fig.cap="(ref:figs5-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs6, cache=!run$figures, fig.height=11, fig.cap="(ref:figs6-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful"),
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

>>>>

```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed"),
  channel_locations = channel_locations,
  p_cluster = p_cluster
)
```

@@

```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"),
  channel_locations = channel_locations,
  p_cluster = p_cluster
)
```

@@

```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"),
  channel_locations = channel_locations,
  p_cluster = p_cluster
)
```

@@

```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"),
  channel_locations = channel_locations,
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs5, cache=!run$figures, fig.height=11, fig.cap="(ref:figs5-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"),
  channel_locations = channel_locations,
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```

@@

```{r, figs6, cache=!run$figures, fig.height=11, fig.cap="(ref:figs6-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful"),
  channel_locations = channel_locations,
  p_cluster = p_cluster,
  conditions = c("Informed", "Unsuccessful")
)
```
